\pkg{cleanR}: Maid for Cleaning Datasets in \proglang{R}

### 2016-12-30 latex/article_vol2.tex
Added example data + documentation

\subsubsection{Calling the new summarize/visualize/check functions from clean()}
Now, we are ready to use these new functions in a \R{clean()}
call. The extended \pkg{cleanR} output document should have the
following modifications, relative to the standard \pkg{cleanR} output:
\begin{itemize}
\item We want to add the new pre-check function, \R{isID}, to the already existing pre-checks.
\item We wish to change the plot type for all variables to the new mosaic plot.
\item We want the new summary function, \R{countZeros}, to be added to the summaries performed on all variable types but \R{Date} and \R{logical}.
\item We want the new check function, \R{identifyColon}, to be added to the checks performed on \R{character}, \R{factor} and \R{labelled} variables.
\end{itemize}
These options are specified as follows: \hl{Jeg synes ikke testData egner sig her. Der er ingen koloner og CPRvar er et mærkeligt, internt navn, hvis ikke man kender danske CPR-numre. Langt de fleste variable har desuden ingen nuller. Måske skal der laves et nyt datasæt?}
\begin{Schunk}
\begin{Sinput}
> data(testData) 
> clean(testData, 
      # Add the new pre-check function
      preChecks = c("isKey", "isEmpty", "isID"),
      # Change the visual
      allVisuals = "mosaicVisual",
      # Add the new summary for specified data types
      characterSummaries = c(defaultCharacterSummaries(), "countZeros"),
      factorSummaries = c(defaultFactorSummaries(), "countZeros"),
      labelledSummaries = c(defaultLabelledSummaries(), "countZeros"),
      numericSummaries = c(defaultNumericSummaries(), "countZeros"),
      integerSummaries = c(defaultIntegerSummaries(), "countZeros"),
      # Add the new check for specific data types
      characterChecks = c(defaultCharacterChecks(), "identifyColons"),
      factorChecks = c(defaultFactorChecks(), "identifyColons"),
      labelledCheck = c(defaultLabelledChecks(), "identifyColons"))
\end{Sinput}
\end{Schunk}
The outputted document is found in Appendix \ref{sec:appendix2}.

@@

\section{Appendix B: User-extended cleaning of  testData} \label{sec:appendix2}
\includepdf[pages=2-, pagecommand={}, frame=true, noautoscale=true, scale=0.7]{cleanR_testData.pdf}
%\hl{Data cleaning with user supplied extensions here}

>>>>

\subsubsection{Calling the new summarize/visualize/check functions from clean()}
Now, we are ready to use these new functions in a \R{clean()}
call. The extended \pkg{cleanR} output document should have the
following modifications, relative to the standard \pkg{cleanR} output:
\begin{itemize}
\item We want to add the new pre-check function, \R{isID}, to the already existing pre-checks.
\item We wish to change the plot type for all variables to the new mosaic plot.
\item We want the new summary function, \R{countZeros}, to be added to the summaries performed on all variable types but \R{Date} and \R{logical}.
\item We want the new check function, \R{identifyColon}, to be added to the checks performed on \R{character}, \R{factor} and \R{labelled} variables.
\end{itemize}
These options are specified as follows: %\hl{Jeg synes ikke testData egner sig her. Der er ingen koloner og CPRvar er et mærkeligt, internt navn, hvis ikke man kender danske CPR-numre. Langt de fleste variable har desuden ingen nuller. Måske skal der laves et nyt datasæt?}
\begin{Schunk}
\begin{Sinput}
> data(exampleData) 
> clean(exampleData, 
      # Add the new pre-check function
      preChecks = c("isKey", "isEmpty", "isID"),
      # Change the visual
      allVisuals = "mosaicVisual",
      # Add the new summary for specified data types
      characterSummaries = c(defaultCharacterSummaries(), "countZeros"),
      factorSummaries = c(defaultFactorSummaries(), "countZeros"),
      labelledSummaries = c(defaultLabelledSummaries(), "countZeros"),
      numericSummaries = c(defaultNumericSummaries(), "countZeros"),
      integerSummaries = c(defaultIntegerSummaries(), "countZeros"),
      # Add the new check for specific data types
      characterChecks = c(defaultCharacterChecks(), "identifyColons"),
      factorChecks = c(defaultFactorChecks(), "identifyColons"),
      labelledCheck = c(defaultLabelledChecks(), "identifyColons"))
\end{Sinput}
\end{Schunk}
The outputted document is found in Appendix \ref{sec:appendix2}.

@@

\section{Appendix B: User-extended cleaning of  testData} \label{sec:appendix2}
\includepdf[pages=2-, pagecommand={}, frame=true, noautoscale=true, scale=0.7]{cleanR_exampleData.pdf}
%\hl{Data cleaning with user supplied extensions here}
